---
title: "Optimal Design under Second-order Least Squares Estimator"
author: | 
  | Chi-Kuang Yeh and Julie Zhou
  | University of Waterloo and University of Victoria
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: yes
  rmarkdown::html_document:
    toc: yes
    toc_float: true
    theme: readable
    highlight: tango
vignette: >
  %\VignetteIndexEntry{designSLSE}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<!-- latex macros -->
\newcommand{\cv}{\operatorname{cv}}

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE
)
options(digits = 3)
```

# Installation

```{r load package}
# required dependencies
require(designSLSE)
require(CVXR)
require(tibble)
require(dplyr)
require(pracma)
require(gridExtra)
```

# Specify the input for the program

1. **N**: Number of design points

2. **S**: The design space

3. **tt**: The level of skewness

4. **$\theta$**: The parameter vector

5. **FUN**: The function for calculating the derivatives of the given model

```{r Define inputs, cache = TRUE}
N <- 101
S <- c(0, 180)
tt <- 0
theta <- c(0.05, 0.5)

FUN <- function(xi, theta){
  deno <- (theta[1] + xi * theta[2])^2
  rbind(-xi/deno, -xi^2/deno)
}

u <- seq(from = S[1], to = S[2], length.out = N)

res <- Aopt(N = N, u = u, tt = tt, FUN = FUN, 
            theta = theta)

```


# Manage the outputs

## Showing the support points 

```{r output}
res$design %>% filter(weight > 1E-4)

```

## Now we want to plot the weights
```{r weight}
plot_weight(res$design)
```

## Plot the directional derivative to use the equivalence theorem


```{r directional}
calc_A <- function(theta, FUN, design){
  
  u <- design$location
  w_hat <- design$weight
  n <- length(theta)
  g1 <- matrix(0, n, 1)
  G2 <- matrix(0, n, n)

  for (i in 1:N) {
    f <- FUN(u[i], theta)
    g1 <- g1 + w_hat[i] * f
    G2 <- G2 + w_hat[i] * f %*% t(f)
  }

  rbind(cbind(1, sqrt(tt) * t(g1)),
        cbind(sqrt(tt) * g1, G2))
}

A <- calc_A(theta = theta, FUN = FUN, design = res$design)

phi_A <- calc_phiA(design = res$design, theta = theta, FUN = FUN, tt = tt, A = A)
AI <- solve(A)
# C <- pracma::blkdiag(matrix(0), diag(1, n))
# penality <- sum(diag(C * AI * t(C)))
plot_direction_Aopt(design = res$design, tt = tt, FUN = FUN, 
                    A = A, phi = phi_A, theta = theta)
```

